---
title: "Biden Polling"
format: html
execute: 
  echo: false
---

```{r}
#| message: false
library(tidyverse)
library(tidymodels)
library(broom)
library(marginaleffects)
poll_data <- tibble(biden = as.factor(c(rep("Yes", 655), 
                                        rep("No", 904)))) |> 
                slice_sample(prop = 1)
              
```



\[
\log \left( \frac{\Pr(Y = 1)}{1 - \Pr(Y = 1)} \right) = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \cdots
\]


\[
\widehat{\text{logit}(\Pr(\text{biden} = \text{"Yes"}))} = -0.469 + 0.723 \cdot \text{age65plus}
\]





```{r}
fit_biden <- logistic_reg() |> fit(biden ~ 1, data = poll_data)
```

```{r}
#| cache: true
fit_biden <- logistic_reg() |> 
  fit(biden ~ 1, data = poll_data)
```

```{r}
library(broom)
library(knitr)
library(dplyr)

tidy(fit_biden, conf.int = TRUE) |>
  select(term, estimate, conf.low, conf.high) |>
  kable(
    caption = "Estimated Log-Odds of Biden Support (Intercept Only Model)\nSource: March 2024 YouGov Poll",
    digits = 3
  )

```

```{r}
library(tidyverse)
library(marginaleffects)

avg_predictions(fit_biden, type = "prob") |>
  filter(group == "Yes") |>
  ggplot(aes(x = group, y = estimate, ymin = conf.low, ymax = conf.high)) +
  geom_pointrange(color = "#2C3E50", size = 1.0) +
  labs(
    title = "Support for President Biden in March 2024",
    subtitle = "42% is not a good sign for an incumbent seeking reelection",
    caption = "Source: YouGov poll, March 2024.",
    x = NULL, y = NULL
  ) +
  scale_x_discrete(labels = NULL, breaks = NULL) +
  scale_y_continuous(
    labels = scales::percent_format(accuracy = 1),
    limits = c(0.38, 0.46)
  )

```

People’s voting preferences are often influenced by a mix of personal characteristics and political leanings, making them both meaningful and unpredictable. Using a March 2024 survey of 1,559 U.S. adults, we examine which individuals say they would vote for Joe Biden if the election were held today.We model voter support for Biden—measured as a binary outcome (Yes/No)—as a logistic function of a constant term, estimating the overall likelihood of support across the population.Based on our model, we estimate that approximately 42% of U.S. adults support Biden, with a 95% confidence interval ranging from 40% to 45%, reflecting the uncertainty inherent in our sample-based inference.

